Convergence rate of MAP estimates \\ for the exponential family

### 2021-11-09 aistats.tex
Fix affiliations

% If your paper is accepted and the title of your paper is very long,
% the style will print as headings an error message. Use the following
% command to supply a shorter title of your paper so that it can be
% used as headings.
%
%\runningtitle{I use this title instead because the last one was very long}

@@

\aistatsauthor{R\'emi Le Priol \And Frederik Kunstner \And  Damien Scieur \And Simon Lacoste-Julien \TODO{s} }

\aistatsaddress{ 
	Mila, Université de Montreal 
	\And  University of \\ British Columbia
	\And SAIT AI Lab, Montreal 
	\And Mila, Université de Montreal \\
	Canada CIFAR AI Chair \\
	SAIT AI Lab, Montreal}
]

>>>>

% If your paper is accepted and the title of your paper is very long,
% the style will print as headings an error message. Use the following
% command to supply a shorter title of your paper so that it can be
% used as headings.
%
\runningtitle{Convergence Rates for the MAP of an Exponential Family and SMD -- an Open Problem}

@@

\aistatsauthor{R\'emi Le Priol \And Frederik Kunstner}
\aistatsaddress{ 
	Mila, Université de Montreal 
	\And  University of British Columbia
	}

\aistatsauthor{Damien Scieur \And Simon Lacoste-Julien}
\aistatsaddress{SAIT AI Lab, Montreal 
	\And Mila, Université de Montreal \\
	SAIT AI Lab, Montreal\\
	Canada CIFAR AI Chair
}

]
